%
% Template for Doctoral Theses at Uppsala 
% University. The template is based on    
% the layout and typography used for      
% dissertations in the Acta Universitatis 
% Upsaliensis series                      
% Ver 5.2 - 2012-08-08                  
% Latest version available at:            
%   http://ub.uu.se/thesistemplate            
%                                         
% Support: Wolmar Nyberg Akerstrom        
% Thesis Production           
% Uppsala University Library              
% avhandling@ub.uu.se                          
%                                         
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\documentclass{UUThesisTemplate}
% Nomenclature


% Package to determine wether XeTeX is used
\usepackage{ifxetex}

\ifxetex
	% XeTeX specific packages and settings
	% Language, diacritics and hyphenation
	\usepackage[babelshorthands]{polyglossia}
	\setmainlanguage{english}
	\setotherlanguages{swedish}

	% Font settings
	\setmainfont{Times New Roman}
	\setromanfont{Times New Roman}
	\setsansfont{Arial}
	\setmonofont{Courier New}
\else
	% Plain LaTeX specific packages and settings
	% Language, diacritics and hyphenation
    % Use English and Swedish languages. 
	\usepackage[swedish,english]{babel} 

	% Font settings
	\usepackage{type1cm}
	\usepackage{inputenc}
	\usepackage[T1]{fontenc}
	\usepackage{mathptmx}
	
	% Enable scaling of images on import
	\usepackage{graphicx}
\fi

% Tables
\usepackage{booktabs}
\usepackage{tabularx}

% Document links and bookmarks
\usepackage{hyperref} 

% Numbering of headings down to the subsection level
\numberingdepth{subsection}

% Including headings down to the subsection level in contents
\contentsdepth{subsection}
\setlength{\parindent}{0pt}
\usepackage{parskip}

\usepackage{biblatex}
\addbibresource{References.bib}

% Subfigures
\usepackage{caption}
\usepackage{subcaption, wrapfig, graphicx}
\usepackage[section]{placeins}

% Maths
\usepackage{amsmath,physics, esint, amssymb}
\usepackage{nicematrix}
\renewcommand{\arraystretch}{1.5} % More spacious tables
\usepackage{algorithm}
\usepackage{algpseudocodex}

% Tikz
\usepackage{tikz}
\usetikzlibrary{shapes.geometric, arrows}

% Custom defines
\input{defines.tex}

% Glossary
\usepackage[toc,section=chapter]{glossaries}
\newglossary{unit}{unit}{unt}{Units}
\renewcommand{\glsclearpage}{}
\loadglsentries{glossary.tex}
\makeglossaries
\glsaddall[types={unit}]


% Uncomment to use a custom abstract dummy text
\abstractdummy{
	\begin{abstract}
		At the European Institute for Nuclear Research, CERN, a new electron
		cooler is being commissioned for the Antiproton Decelerator experiment.
		In this experiment protons are shot into a block of metal, which creates
		anti protons. These anti protons will thereafter be focused into 
		a particle beam, a process done in several steps. One of these steps
		is with an electron cooler.
		This cooler shoots electrons into the ion-beam path. These electrons then
		collide with the beam particles, and momentum is transferred from the 
		beam particles to the electrons. The electrons are then steered away
		from the beam path, into an electron collector.

		In the beam path drift of the cooler, where the anti protons and 
		electrons meet, a normal conducting solenoid magnet is used to
		orient the electron path. This magnet comes with strict requirements on
		field quality, in the order of $\vec{B}_\perp / \vec{B}_\parallel < 10$ppm.

		In this thesis a metrological characterization of a prototype measurement
		system for solenoidal magnets is presented. Instead of winding measurement
		coils with wire, they are instead printed on a circuit board over ten 
		layers. Of particular interest was the magnet alignment with respect to
		the beam aperture, so that the magnetic solenoid axis is in line
		with the aperture central axis. For this purpose, a mathematical model
		for solenoidal magnetic fields has been constructed. This model can be
		used to quantify the sensitivity of the measurement system for an
		unaligned magnet. Furthermore, some test measurements are presented, 
		along with some simulation campaigns to further characterize the problem.
		A specific method where the magnetic field peaks are used to measure 
		the alignment is evaluated.
	\end{abstract}
}

\begin{document}
\frontmatter
% Creates the front matter (title page(s), abstract, list of papers)
% for either a Comprehensive Summary or a Monograph.
% Authors of Comprehensive Summaries use this front matter 
\frontmatterCS
% Monograph authors use this front matter 
%\frontmatterMonograph 
\newpage
\section*{Sammanfattning på Svenska}
På den Europeiska organisationen för Kärnforskning pågår just
nu ett uppgraderingsarbete för AD-experimentet, (fullständigt
namn på engelska: Antiproton Decelerator). I detta experiment
skjuts protoner in i ett block med metall, vilket skapar 
antiprotoner. Dessa antiprotoner ska sedan fokuseras till
en partikelstråle, vilket görs i en rad olika steg, däribland
med vad som kallas för en elektronkylare. Elektronkylaren
skjuter in elektroner i partikelstrålens väg, vilka kolliderar
med antiprotonerna och på detta sätt reducerar temperaturen
i partikelstrålen genom att överföra momentum till elektronerna.

Elektronerna leds sedan bort ur strålens väg, in i en elektronsamlare.
I strålaperturen, där elektronerna och antiprotonerna möts, används
en normalledande solenoidmagnet för att styra elektronerna. Denna
solenoidmagnet kommer med strikta krav på den magnetiska fältprofilen,
varför känslig mätutrustning krävs. Det magnetiska fältet måste
vara av solenoid karaktär, så att $\vec{B}_\perp / \vec{B}_\parallel < 10$ppm.

I denna rapport presenteras en metrologisk karaktärisering av en
ny prototyp på mätsystem för solenoidmagneter. Istället för att linda spolar som en mäter
fältkvalitén med, så har dessa istället tryckts på ett kretskort över
tio lager. Av speciellt intresse var att mäta magnetens justering, så
att solenoidaxeln ligger i linje med strålaperturen. För detta ändamål
så har en matematisk modell för solenoida magnetfält konstruerats. Denna
modell kan användas för att kvantifiera känsligheten hos mätsystemet
för en ojusterad solenoidmagnet. Vidare så presenteras testmätningar
med systemet, samt en rad simulationer för att vidare karaktärisera problemet.
En specifik mätmetodik där magnetfältstopparna används för att undersöka 
magnetens justering utvärderas.


% Optional dedication
\dedication{Thanks to everyone at the TE-MSC-MM department for their warm and
inviting culture, and sharing all
their knowledge on magnetics. Thanks especially to my supervisors Carlo Petrone
and Mariano Pentella, who taught me everything you could want to know about
Italy.}

% Environment used to create a list of papers
%\begin{listofpapers}
%	\item A Paper Discussed in this Thesis \label{apaperlabel}
%\end{listofpapers}



\begingroup
% To adjust the indentation in your table of contents, uncomment and enter the widest numbers for each level
%  E.g.  \settocnumwidth{widest chapter number}{widest section number}{widest subsection number}...{...}
%  \settocnumwidth{5}{4}{5}{3}{3}{3}
\tableofcontents
\endgroup

% Optional tables
%\listoftables
%\listoffigures

\mainmatter
% This includes the "Instruction", "Problem and Solutions" and "Example" files. After reading it, remove it from Thesis.tex. 

% Include your chapters here.

\input{Chapters/Introduction.tex}
\input{Chapters/Theory.tex}
\input{Chapters/coil-magnetometer.tex}
\input{Chapters/measurements.tex}
\input{Chapters/simulations.tex}
\input{Chapters/post_processing.tex}
\input{Chapters/discussion.tex}
\clearpage


\backmatter
% References
% No restriction is set to the reference styles
% Save your references in References.bib
\nocite{*} % Remove this for your own citations
\printglossary[type=main]
\printglossary[type=unit]
%\bibliographystyle{plain}
%\bibliography{References}
\printbibliography
\end{document}